lnc34a splice junctions

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
more of the previous commit 5

url <- "figure2b_HctHekDox.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure2b_HctHekDox/figure2b_HctHekDox.pdf"

>>>>

url <- fileMap(type = "rds")["figure2b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
more of the previous commit 5

url <- "figure2a_HCT116p53null.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"

>>>>

url <- fileMap(type = "rds")["figure2a"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
more of the previous commit 5

```{r, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject",
    "ggthemes"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

@@

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
  url <- "suppFigure2d_lnc34aCage.txt"
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(14) %>% 
    gsub(
      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCage(.*)Cell.*", 
      "\\1",
      .
    ) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
  url <- "suppFigure2d_lnc34aCage.rds"
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(filename) %>%
    gsub(
      "^wgEncodeRikenCage(.*)Cell.*",
      "\\1",
      .
    ) %>%
    unique()
}
```

All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDA.R file. Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200). These cell lines included: `r cellLinesInFinal()`. All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance. In addition, a density plot shows the distribution of the CAGE reads at in the specified interval.

@@

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2d_lnc34aCage.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(
      y = 1:length(pull(., level)),
      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
    )

@@

path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2d_lnc34aCage/suppFigure2d_lnc34aCage.pdf"
ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

```{r, message = FALSE}

packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject",
    "ggthemes"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure2d"][[1]]

  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(14) %>% 
    gsub(
      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCage(.*)Cell.*", 
      "\\1",
      .
    ) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure2d"][[1]]

  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(filename) %>%
    gsub(
      "^wgEncodeRikenCage(.*)Cell.*",
      "\\1",
      .
    ) %>%
    unique()
}
```

All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file. Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200). These cell lines included: `r cellLinesInFinal()`. All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance. In addition, a density plot shows the distribution of the CAGE reads at in the specified interval.

@@

url <- fileMap(type = "rds")["suppFigure2d"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(
      y = 1:length(pull(., level)),
      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
    )

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
more of the previous commit 5

```{r, echo = FALSE, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

@@

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
  url <- "suppFigure2e_lnc34aSplJnc.txt"
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(16) %>% 
    gsub(
      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeq(.*)Cell.*", 
      "\\1",
      .
    ) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
  url <- "suppFigure2e_lnc34aSplJnc.rds"
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(filename) %>%
    gsub(
      "^wgEncodeCshlLongRnaSeq(.*)Cell.*",
      "\\1",
      .
    ) %>%
    unique()
}
```

All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDA.R file. Of these cell lines `r cellLinesInFinal() %>% length()` cell lines had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region). Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`. All splice junctions were plotted and colored according to the number of reads corresponding to each.

@@

#splice junctions
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2e_lnc34aSplJnc.rds"
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.pdf"
ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)

>>>>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure2e"][[1]]

  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(16) %>% 
    gsub(
      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeq(.*)Cell.*", 
      "\\1",
      .
    ) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure2e"][[1]]

  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(filename) %>%
    gsub(
      "^wgEncodeCshlLongRnaSeq(.*)Cell.*",
      "\\1",
      .
    ) %>%
    unique()
}
```

All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file. Of these cell lines `r cellLinesInFinal() %>% length()` cell lines had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region). Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`. All splice junctions were plotted and colored according to the number of reads corresponding to each.

@@

#splice junctions
url <- fileMap(type = "rds")["suppFigure2e"][[1]]
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
